Evaluation of performances

### 2020-03-03 analysis/eval-performance.Rmd
wflow_publish(knitr_in("analysis/eval-performance.Rmd"), view = FALSE, verbose = TRUE)

```{r}
df_perf <- getBMRPerformances(bm_aggregated_new_buffer2, as.df = T) %>%
  mutate(task.id = recode_factor(task.id,
    `hr_buffer2` = "HR",
    `vi_buffer2` = "VI",
    `nri_buffer2` = "NRI",
    `nri_vi_buffer2` = "NRI_VI",
    `hr_nri_buffer2` = "HR-NRI",
    `hr_vi_buffer2` = "HR-VI",
    `hr_nri_vi_buffer2` = "HR-NRI-VI",
  )) %>%
  tidyr::separate(learner.id, c("learner_group", "filter"),
    remove = FALSE,
    sep = " MBO "
  )
```

Aggregate performances and add standard error column.

```{r aggr-perf}
df_perf %<>%
  group_by(task.id, learner.id, filter) %>%
  mutate(rmse_aggr = round(mean(rmse), 3)) %>%
  mutate(se = round(sd(rmse), 3)) %>%
  select(-rmse, iter) %>%
  ungroup()
```

@@

## (Plot) P2 Best filter combination of each learner vs. no filter per task vs. Borda

**DEPRECATED**: Please see the scatterplots below for a better visulization

Showing the final effect of applying feature selection to a learner for each task.
The more left a certain filter appears for a given task compared to the purple dot (No Filter), the higher the effectivity of applying feature selection for that given learner on the given task.

```{r filter-effect-best-vs-no-filter, warning=FALSE, dev = c("png", "pdf")}
# we rbind two filtered data.frames
# doing the filtering in one step is (at least) complicated here

best_filter <- df_perf %>%
  mutate(filter = replace(filter, is.na(filter), "No Filter")) %>%
  dplyr::filter(filter != "No Filter") %>%
  group_by(learner_group, task.id) %>%
  dplyr::filter(learner_group == "SVM" | learner_group == "RF" | learner_group == "XGBoost") %>%
  slice(which.min(rmse_aggr))

best_no_filter <- df_perf %>%
  mutate(task.id = recode_factor(task.id,
    `hr` = "HR",
    `vi` = "VI",
    `nri` = "NRI",
    `nri_vi` = "NRI_VI",
    `hr_nri` = "HR-NRI",
    `hr_vi` = "HR-VI",
    `hr_nri_vi` = "HR-NRI-VI",
  )) %>%
  tidyr::separate(learner.id, c("learner_group", "filter"),
    remove = FALSE,
    sep = " MBO "
  ) %>%
  mutate(filter = replace(filter, is.na(filter), "No Filter")) %>%
  dplyr::filter(filter == "No Filter") %>%
  group_by(learner_group, task.id) %>%
  dplyr::filter(learner_group == "SVM" | learner_group == "RF" | learner_group == "XGBoost") %>%
  slice(which.min(rmse_aggr))

comb <- bind_rows(best_filter, best_no_filter)

comb %>%
  ggplot(aes(x = rmse_aggr, y = learner_group)) +
  geom_beeswarm(groupOnX = FALSE, aes(color = filter), size = 3) +
  facet_wrap(~task.id) +
  # scale_color_nejm() +
  labs(x = "RMSE", y = "Task", color = "Filter") +
  guides(size = FALSE) +
  scale_x_continuous(limits = c(27, 47)) +
  theme_pubr() +
  theme(
    panel.grid.major.y = element_line(size = 0.1, linetype = "dashed"),
    axis.title.y = element_blank(),
    axis.text.y = element_text(angle = 45),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    plot.margin = unit(c(6, 6, 6, 0), "pt")
  )
```

## (Plot) P3 Best filter combination of each learner vs. Borda filter

Showing the final effect of the ensemble Borda filter vs the best scoring simple filter.

```{r filter-effect-ensemble, warning=FALSE}
# we rbind two filtered data.frames
# doing the filtering in one step is (at least) complicated here

best_filter <- df_perf %>%
  mutate(filter = replace(filter, is.na(filter), "No Filter")) %>%
  dplyr::filter(filter != "No Filter") %>%
  group_by(learner_group, task.id) %>%
  dplyr::filter(learner_group == "SVM" | learner_group == "RF" | learner_group == "XGBoost") %>%
  slice(which.min(rmse_aggr))

borda <- df_perf %>%
  mutate(filter = replace(filter, is.na(filter), "No Filter")) %>%
  dplyr::filter(filter == "Borda") %>%
  group_by(learner_group, task.id) %>%
  dplyr::filter(learner_group == "SVM" | learner_group == "RF" | learner_group == "XGBoost") %>%
  slice(which.min(rmse_aggr))

comb_borda <- bind_rows(best_filter, borda)

comb_borda %>%
  ggplot(aes(x = rmse_aggr, y = learner_group)) +
  geom_beeswarm(groupOnX = FALSE, aes(color = filter), size = 3) +
  facet_wrap(~task.id) +
  scale_color_nejm() +
  labs(x = "RMSE", y = "Task", color = "Filter") +
  guides(size = FALSE) +
  scale_x_continuous(limits = c(27, 47)) +
  theme_pubr() +
  theme(
    panel.grid.major.y = element_line(size = 0.1, linetype = "dashed"),
    axis.title.y = element_blank(),
    axis.text.y = element_text(angle = 45),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
    plot.margin = unit(c(6, 6, 6, 0), "pt")
  )
```

## (Plot) P4 Performances of all filter methods

```{r filter-perf-all, warning=FALSE, dev = c("png", "pdf")}
# perf_all_filters <- df_perf %>%
#   mutate(filter = replace(filter, is.na(filter), "No Filter")) %>%
#   dplyr::filter(filter != "No Filter") %>%
#   group_by(learner_group, task.id) %>%
#   dplyr::filter(learner_group == "SVM" | learner_group == "RF" | learner_group == "XGBoost") %>%
#   slice(which.min(rmse_aggr))
#   summarise(perf = mean(rmse_aggr), filter = as.character(filter))
#
# perf_all_filters %>%
#   ggplot(aes(x = rmse_aggr, y = learner_group)) +
#   geom_beeswarm(groupOnX = FALSE, aes(color = filter), size = 2) +
#   facet_wrap(~task.id) +
#   scale_color_nejm() +
#   labs(x = "RMSE", y = "Task", color = "Filter") +
#   guides(size = FALSE) +
#   scale_x_continuous(limits = c(30, 45)) +
#   theme_pubr() +
#   theme(
#     panel.grid.major.y = element_line(size = 0.1, linetype = "dashed"),
#     axis.title.y = element_blank(),
#     axis.text.y = element_text(angle = 45),
#     legend.text = element_text(size = 12),
#     legend.title = element_text(size = 12),
#     plot.margin = unit(c(6, 6, 6, 0), "pt")
#   )
```

## (Plot) P5 Scatterplots of filter methods vs. no filter for each learner and task

@@

```{r filter-effect-all-vs-no-filter, warning=FALSE, dev = c("png", "pdf")}
results_aggr1 <- df_perf %>%
  filter(learner_group != "Ridge-CV") %>%
  filter(learner_group != "Lasso-CV") %>%
  # mutate(filter = replace(filter, "No Filter", "NF")) %>%
  mutate(learner_group = as.factor(learner_group)) %>%
  mutate(learner_group = recode(learner_group, `XGBoost` = "XG")) %>%
  mutate(filter = recode(filter, `No Filter` = "NF")) %>%
  mutate(learner_group = fct_rev(learner_group)) %>%
  group_by(learner_group, task.id, filter) %>%
  # we actually took the mean already in chunk 'aggr-perf'. This is only to get
  # summarise() working
  summarise(perf = mean(rmse_aggr))

@@

## (Plot) P6 Scatterplots of filter methods vs. Borda for each learner and task

@@

```{r filter-effect-all-vs-borda-filter, warning=FALSE, dev = c("png", "pdf")}
results_aggr2 <- df_perf %>%
  na.omit() %>%
  filter(learner_group != "Ridge-CV") %>%
  filter(learner_group != "Lasso-CV") %>%
  mutate(learner_group = recode_factor(learner_group, `XGBoost` = "XG")) %>%
  group_by(learner_group, task.id, filter) %>%
  # we actually took the mean already in chunk 'aggr-perf'. This is only to get
  # summarise() working
  summarise(perf = mean(rmse_aggr)) %>%
  ungroup()

results_aggr2 %>%
  ggplot(aes(x = perf, y = fct_reorder(learner_group, -perf))) +
  geom_beeswarm(
    data = results_aggr2[results_aggr2$filter != "Borda", ],
    shape = 3, size = 1.1, aes(color = "Filter"),
    groupOnX = FALSE
  ) +
  geom_point(
    data = results_aggr2[results_aggr2$filter == "Borda", ],
    shape = 19, size = 2, aes(color = "Borda Filter")
  ) +
  facet_wrap(~task.id) +
  scale_color_manual(
    guide = guide_legend(override.aes = list(shape = c(19, 3))),
    values = c(
      "Filter" = "#BC3C29FF",
      "Borda Filter" = "#0072B5FF"
    )
  ) +
  labs(x = "RMSE", y = "Task", colour = NULL) +
  guides(size = FALSE) +
  scale_x_continuous(limits = c(27, 51)) +
  theme_pubr() +
  theme(
    panel.grid.major.y = element_line(size = 0.1, linetype = "dashed"),
    axis.title.y = element_blank(),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
  )
```

>>>>

```{r, warning = FALSE}
df_perf <- getBMRPerformances(bm_aggregated_new_buffer2, as.df = T) %>%
  mutate(task.id = recode_factor(task.id,
    `hr_buffer2` = "HR",
    `vi_buffer2` = "VI",
    `nri_buffer2` = "NRI",
    `nri_vi_buffer2` = "NRI_VI",
    `hr_nri_buffer2` = "HR-NRI",
    `hr_vi_buffer2` = "HR-VI",
    `hr_nri_vi_buffer2` = "HR-NRI-VI",
  )) %>%
  tidyr::separate(learner.id, c("learner_group", "filter"),
    remove = FALSE,
    sep = " MBO "
  )
```

```{r aggr-perf}
# Aggregate performances and add standard error column.
df_perf %<>%
  group_by(task.id, learner.id, filter) %>%
  mutate(rmse_aggr = round(mean(rmse), 3)) %>%
  mutate(se = round(sd(rmse), 3)) %>%
  select(-rmse, iter) %>%
  ungroup()
```

@@

## (Plot) P2 Scatterplots of filter methods vs. no filter for each learner and task

@@

```{r filter-effect-all-vs-no-filter, warning=FALSE, dev = c("png", "pdf")}
results_aggr1 <- df_perf %>%
  filter(learner_group != "Ridge-CV") %>%
  filter(learner_group != "Lasso-CV") %>%
  # mutate(filter = replace(filter, "No Filter", "NF")) %>%
  mutate(learner_group = as.factor(learner_group)) %>%
  mutate(learner_group = recode(learner_group, `XGBoost` = "XG")) %>%
  mutate(filter = recode(filter, `No Filter` = "NF")) %>%
  mutate(learner_group = fct_rev(learner_group)) %>%
  group_by(learner_group, task.id, filter) %>%
  # we actually took the mean already in chunk 'aggr-perf'. This is only to get
  # summarise() working
  summarise(perf = mean(rmse_aggr)) %>% 
  ungroup() %>% 
  # we need to reverse the order on porpuse here so that ggplot reverses it
  # again later
  mutate(learner_group = fct_relevel(learner_group, "XGBOOST", "SVM", "RF"))

@@

## (Plot) P3 Scatterplots of filter methods vs. Borda for each learner and task

@@

```{r filter-effect-all-vs-borda-filter, warning=FALSE, dev = c("png", "pdf")}
results_aggr2 <- df_perf %>%
  na.omit() %>%
  filter(learner_group != "Ridge-CV") %>%
  filter(learner_group != "Lasso-CV") %>%
  mutate(learner_group = recode_factor(learner_group, `XGBoost` = "XG")) %>%
  group_by(learner_group, task.id, filter) %>%
  # we actually took the mean already in chunk 'aggr-perf'. This is only to get
  # summarise() working
  summarise(perf = mean(rmse_aggr)) %>%
  ungroup() %>% 
  # we need to reverse the order on porpuse here so that ggplot reverses it
  # again later
  mutate(learner_group = fct_relevel(learner_group, "XGBOOST", "SVM", "RF"))

results_aggr2 %>%
  ggplot(aes(x = perf, y = learner_group)) +
  geom_beeswarm(
    data = results_aggr2[results_aggr2$filter != "Borda", ],
    shape = 3, size = 1.1, aes(color = "Filter"),
    groupOnX = FALSE
  ) +
  geom_point(
    data = results_aggr2[results_aggr2$filter == "Borda", ],
    shape = 19, size = 2, aes(color = "Borda Filter")
  ) +
  facet_wrap(~task.id) +
  scale_color_manual(
    guide = guide_legend(override.aes = list(shape = c(19, 3))),
    values = c(
      "Filter" = "#BC3C29FF",
      "Borda Filter" = "#0072B5FF"
    )
  ) +
  labs(x = "RMSE", y = "Task", colour = NULL) +
  guides(size = FALSE) +
  scale_x_continuous(limits = c(27, 51)) +
  theme_pubr() +
  theme(
    panel.grid.major.y = element_line(size = 0.1, linetype = "dashed"),
    axis.title.y = element_blank(),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 12),
  )
```
